---
title: "School Board Cluster"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, comment = "", fig.align = "center", fig.width = 9, fig.height = 9)

library(dplyr)

library(factoextra)

load("clustering.RData")
```


## Visualizing Correlations

```{r}
clusterData %>% 
  select(-school_district, -sale_price, -LRSN) %>% 
  na.omit() %>% 
  cor() %>% 
  ggcorrplot::ggcorrplot(., hc.order = TRUE,
                         outline.col = "white",
                         ggtheme = ggplot2::theme_minimal,
                         colors = c("#6D9EC1", "white", "#E46726"))
```

For the sake of producing tidier clusters, we are going to drop a few highly-correlated variables. 

## Medoids By School District

As a first pass, the 2017 data was split based upon school district. Data within each school distict was then partitioned into 4 clusters. 

### Cluster Quality

```{r}
data.frame(schoolDistrict = c("JG", "MSC", "NPU", "PHM", "SBCSC", "UNU" ), 
           averageSilhouetteWidth = c(clusNumTest$JG$silinfo$avg.width, 
                                      clusNumTest$MSC$silinfo$avg.width, 
                                      clusNumTest$NPU$silinfo$avg.width, 
                                      clusNumTest$PHM$silinfo$avg.width, 
                                      clusNumTest$SBCSC$silinfo$avg.width, 
                                      clusNumTest$UNU$silinfo$avg.width)) %>% 
  knitr::kable()
```


### John Glenn

```{r}
clusNumTest$JG$medoids %>% knitr::kable(.)

fviz_cluster(clusNumTest$JG, geom = "point", ellipse.type = "norm",
             palette = "jco", ggtheme = theme_minimal())
```


### Mishawaka

```{r}
clusNumTest$MSC$medoids %>% knitr::kable(.)

fviz_cluster(clusNumTest$MSC, geom = "point", ellipse.type = "norm",
             palette = "jco", ggtheme = theme_minimal())
```


### New Prairie United

```{r}
clusNumTest$NPU$medoids %>% knitr::kable(.)

fviz_cluster(clusNumTest$NPU, geom = "point", ellipse.type = "norm",
             palette = "jco", ggtheme = theme_minimal())
```


### Penn-Harris-Madison

```{r}
clusNumTest$PHM$medoids %>% knitr::kable(.)

fviz_cluster(clusNumTest$PHM, geom = "point", ellipse.type = "norm",
             palette = "jco", ggtheme = theme_minimal())
```


### South Bend 

```{r}
clusNumTest$SBCSC$medoids %>% knitr::kable(.)

fviz_cluster(clusNumTest$SBCSC, geom = "point", ellipse.type = "norm",
             palette = "jco", ggtheme = theme_minimal())
```


### Union-North United

```{r}
clusNumTest$UNU$medoids %>% knitr::kable(.)

fviz_cluster(clusNumTest$UNU, geom = "point", ellipse.type = "norm",
             palette = "jco", ggtheme = theme_minimal())
```



## Sales By School District And Cluster

```{r}
clusterAssignmentData %>% 
  mutate(saleNY = ifelse(is.na(sale_price), 0, 1)) %>% 
  group_by(school_district, clusterAssignment) %>% 
  summarize(totalProperties = n(), 
            sold = as.integer(sum(saleNY)), 
            averageSalePrice = round(mean(sale_price, na.rm = TRUE)), 
            averageAV = round(mean(total_AV_roll, na.rm = TRUE))) %>% 
  mutate(percSold = round(sold / totalProperties, 3)) %>% 
  select(school_district, clusterAssignment, totalProperties, sold, 
         percSold, averageAV, averageSalePrice) %>% 
  DT::datatable(.)
```

